---
title: "10-import"
output: html_notebook
---

1. Describe the data and the problem

2. Read in and check data

3. Clean up the data. 

# About the dataset

The dataset recorded the historical sales of a supermarket company with 3 different branches for 3 months. Each row represents one purchase, and each column represents one attribute. The details of the attributes are listed below:

- Invoice id: Computer generated sales slip invoice identification number
- Branch: Branch of supercenter (3 branches are available identified by A, B and C).
- City: Location of supercenters
- Customer type: Type of customers, recorded by Members for customers using member card and Normal for without member card.
- Gender: Gender type of customer
- Product line: General item categorization groups - Electronic accessories, Fashion accessories, Food and - beverages, Health and beauty, Home and lifestyle, Sports and travel
- Unit price: Price of each product in $
- Quantity: Number of products purchased by customer
- Tax: 5% tax fee for customer buying
- Total: Total price including tax
- Date: Date of purchase (Record available from January 2019 to March 2019)
- Time: Purchase time (10am to 9pm)
- Payment: Payment used by customer for purchase (3 methods are available - Cash, Credit card and Ewallet)
- COGS: Cost of goods sold
- Gross margin percentage: Gross margin percentage
- Gross income: Gross income
- Rating: Customer stratification rating on their overall shopping experience (On a scale of 1 to 10)

# Goal

Our goal is to predict the quantity of the items sold per branch in each day.


# Read in and check the data

a. load libraries
```{r load library}
library(readr)
library(tidyverse)
library(lubridate) # date
library(janitor) # clean_names
library(assertr) # assert
```


b. import dataset

```{r import data}
supermarket <- read_csv("supermarket_sales.csv")
```


c. clean names

we use `clean_names()` to clean the volumn names.

```{r clean_names}
supermarket <- clean_names(supermarket)
names(supermarket)
```


d. dimension and the structures

Checking the structures of the data, we find that the dataset has 1000 observations and 17 attributes.
```{r Check the dimensions and the structures}
dim(supermarket)
str(supermarket)
```


e. check NA

```{r Check NA}
supermarket %>% 
  verify(!is.na(.))

```
There is no NA in the dataset.


f. Assert 

Before we start doing data exploration and feature engineering, we need to check whether there exists abnormal values in each variable. Thus we use `assert()` function to detect the abnormalities.

(1)  We want to check whether invoice_id is unique. The result shows that it is.
```{r assert id}
supermarket %>%
  assert(is_uniq, invoice_id)
```


(2) We want to check the following categorical variables.
```{r assert categorical variables}
supermarket %>%
  assert(in_set("A", "B", "C"), branch) %>%  # check whether the dataset contains only three branch
  assert(in_set("Female", "Male"), gender) %>%  # check whether the gender only include male and female
  assert(in_set("Ewallet", "Cash", "Credit card"), payment) # check whether there are more than three types of payment methods which are listed above
```
The dataset looks good!


(3) we want to check the following numerical variables to see if they are in the prospected ranges.
```{r assert numerical variables}
supermarket %>%
  assert(within_bounds(1, 10), rating) %>%  # check the ratings that is assumed to be in 1 to 10.
  assert(within_bounds(0, max(supermarket$unit_price)), unit_price) %>%  # check the unit_price to see whether it is larger than 0.
  assert(within_bounds(0, 100), gross_margin_percentage) # check the gross_margin_percentage to see whether it ranges from 0 to 100.
```

The results show that there is no abnormal value in the dataset.


# Clean up the data

After checking the data, we found that the dataset is almost clean. Now we can do some changes for the type of the variables.

For "date" variable, we know that it is supposed to be Date type instead of char. So we use `mdy()` to make this change.

```{r change the types of date variables}
supermarket$date <- mdy(supermarket$date)
str(supermarket$date)
```

I think the customer type is a good predictor, but naming the values into "0" and "1" will be better for modelling. Thus, I will recode the value for this variable, "1" equals to "Member" and "0" equals to "Normal".

```{r}
supermarket %>%
  mutate(customer_type = ifelse(customer_type == "Member", 1, 0))
```


Now the data looks more clean. Now we can start playing with data!
