---
title: "assign4"
output: html_notebook
---


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 


# Part 1

```{r load library}
library(tidyverse)
library(lubridate)
```


## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 

```{r first day very month}
firstday_every_month <- floor_date(today(), unit = "year") + months(0 : 11)
firstday_every_month
```


Write a function that given your birthday (as a date), returns how old you are in years.

```{r age}
age <- function(birthday) {
  (birthday %--% today()) %/% years()
}

age(ymd(19950225))

```

Write a function that given your birthday, returns the day of the week you were born on. 

```{r born day of the week}
born_week <- function(birthday) {
  (wday(birthday, label=TRUE, abbr = FALSE))
}

born_week(ymd(19950225))

```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)
```{r load library}
library(RVerbalExpressions)
library(stringr)
```


```{r At least seven letters}
words <- stringr::words

# Regular expression
str_view(words, "^\\w{7}(.*)$", match = TRUE) # matching words
str_view(words, "^\\w{7}(.*)$", match = FALSE) # non-matching words


# RVerbalExpression
wordrx_matched <- rx() %>%
  rx_start_of_line() %>% 
  rx_word_char() %>% 
  rx_repeat_previous(7) %>% 
  rx_anything() %>%
  rx_end_of_line() %>% 
  print()

str_view(words, wordrx_matched, match = TRUE) # matching words
str_view(words, wordrx_matched, match = FALSE) # non-matching words

```

## R4DS 14.3.3.1

Use str_detect to find all words that:

(1) That only contain consonants. (Hint: thinking about matching "not"-vowels.)

```{r (1) Consonants}
# Regular expression
words[str_detect(words, "^[^aeiou]+$")]

# RVerbalExpression
in_consonants <- rx() %>% 
  rx_start_of_line() %>% 
  rx_anything_but(c("aeiou")) %>% 
  rx_end_of_line() %>% 
  print()

words[str_detect(words, in_consonants)]

```


(2) Empirically verify the rule "i before e except after c".

```{r (2) i before e except after c}

# Regular expression
words[str_detect(words, "[^c]ie")]

# RVerbalExpression
spell_rule <- rx() %>% 
  rx_something_but("c") %>% 
  rx_find("ie") %>% 
  print()


words[str_detect(words, spell_rule)]

```


(3) Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.

```{r (3) match tel numbers}

# Common format (xxx-xxx-xxxx or xxx.xxx.xxxx): Regular Expression
grepl("^\\d{3}[-\\.]\\d{3}[-\\.]\\d{4}$", "615-319-5166")


# Common format (xxx-xxx-xxxx or xxx.xxx.xxxx): RVerbalExpression

telrx <- rx() %>%
  rx_start_of_line() %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>%
  rx_digit() %>%
  rx_repeat_previous(4) %>% 
  rx_end_of_line() %>% 
  print() %>% 
  grepl(c("615-319-5166", "615.319.5166", "EM5.319.5166","(615)319-5166")) %>% 
  print()

```

```{r (3) Special case}
# Special case ((xxx) xxx-xxxx): Regular Expression
grepl("^(\\()?\\d{3}(\\))?[-\\. ]\\d{3}[-\\.]\\d{4}$", "(615) 319-5166")

# Special case ((xxx) xxx-xxxx): RVerbalExpression
telrx_special <- rx() %>%
  rx_start_of_line() %>% 
  rx_maybe("(") %>%
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_maybe(")") %>%
  rx_any_of("-. ") %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>%
  rx_digit() %>%
  rx_repeat_previous(4) %>% 
  rx_end_of_line() %>% 
  print() %>% 
  grepl(c("615-319-5166", "615.319.5166", "(615) 319-5166")) %>% 
  print()


```


# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

